% $Id: acknowledgements.tex 1784 2012-07-02 15:12:31Z nicolas.cardozo $
% !TEX root = main.tex

\chapter{Acknowledgements}

Having so many to thank in such a small space is daunting, I do not want to skip anyone, nonetheless, I'll try to be succinct.

First and foremost, I would like to thank my advisor, Nicolas Cardozo, for listening to a weird idea from an even weirder student.
His guidance has been incredible, not only in this work, but also in what follows from it.

I also thank the members of the Crypto and PIL groups at the FLAGLab. They gave me a space to talk about printed plastic pieces and
esoteric programming languages. Your feedback and support have been invaluable in shaping this work and the language's technicalities.
Making \sculpt out of 3D printed pieces was a monumental task my poor Ender printer was simply incapable of, and I would like to thank the people at CREA and the guys running the department's 3D printers for their help in making this possible.

I will probably never be as good as a designer as my sister, Sara, but I will always be grateful for
her help in making the \sculpt visual language, posters and documentation look amazing and work as well as they did.
I also owe a lot to my mother, who has always supported me in my endeavors, even when they seem a bit out there, rushing to help with the intense manual labour that went into this endeavour.

I am not very good at organizing in my schedules nor am I the best at keeping track of time. Calendars and to-do lists are not my thing.
I would like to thank my partner, who has been there to mindlessly remind me of deadlines and to keep me on track by simply asking for updates.
Your selfless interest on the project has been a great help in keeping me focused and on track.
I am not sure how you put up with me, but I am glad you do.

At times I have been told that I should be more serious, but I have always been quite aloof.
I would like to thank my friends for putting up with me and my shenanigans, and for always being there to help me out when I needed it.
Always at the ready to make me crack a smile or two when times got rough and my hands numb from hand-sanding every printed piece of \sculpt.

To everyone that played and broke pieces with \sculpt, whether in its beginnings or in its final state. I thank you for your patience and for being willing to try something new.
Your feedback has been invaluable in shaping the language, its ecosystem and the validation for this document.
I hope you enjoyed it as much as I did building it.

Lastly, I want to thank you, the reader, whether obligated or not to read, for taking the effort to push through several pages of me rambling about
a quirky idea that turned into so much more. I encourage you to try it out and code as an artist, or sculpt as a programmer.
\endinput

